Cell Decomposition of Rank 2 Quiver Grassmannians

### 2017-05-09 Grassmannian_cells.tex
Started editing Section 2
This is just to save my changes and to avoid conflicts...

We say that a representation $X\in \Rep(Q)$ can be lifted (to $\tilde Q$) if there exists a representation $\tilde X\in\Rep(\tilde Q)$ such that $F_Q\tilde X=X$ where $F_Q:\Rep(\tilde Q)\to\Rep(Q)$ is the natural functor.
\end{definition}
\begin{lemma}
  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to a representation of $\tilde Q$.
\end{lemma}
\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$. Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the one of $Q$. Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,w)$ of $\tilde Q$. This leads the claim. The statement for preinjective representations follows in the same way.
\end{proof}
We choose a map $d:\tilde Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$. In any case, we can consider the decomposition $X_q=\bigoplus_{w\in W_Q} X_{(q,w)}$. We define a torus action on each $X_{(q,w)}$ via $t.x_{(q,w)}=t^{d(q,w)}x_{(q,w)}$ which can be extended linearly to each $X_q$. For a fixed a subspace $U_q$, we can define the subspace $t.U_q$. In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$. Actually, for this the action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$ and every $x\in X_i$. 
\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
If $X\in\Rep(Q)$ can be lifted, $d:\tilde Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,w\alpha)-d(i,w)=c_\alpha$ for all $\alpha:i\to j$ and $w\in W_{Q}$.
\end{lemma}
\begin{proof} Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,w)}:X_{(i,w)}\to X_{(j,w\alpha)}$. Then the condition $X_{\alpha}(t.U_i)\in t.U_j$ translates into ...to be continued.
\end{proof}

\begin{lemma}
  There exists $d:\tilde Q_0\to\ZZ$ such that $d(q,w)\ne d(q',w')$ for all $q,q',w,w'$ with $\dim X_{q,w}\ne0$ and $\dim X_{q',w'}\ne0$.
\end{lemma}

\begin{theorem}
  $Gr^Q_\bfe(X)^T\cong\bigsqcup_{\tilde\bfe of type \bfe} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$
\end{theorem}

>>>>

We say that a representation $X\in \Rep(Q)$ can be lifted (to $\tilde Q$) if there exists a representation $\tilde X\in\Rep(\tilde Q)$ such that $F_Q\tilde X=X$ where $F_Q:\Rep(\tilde Q)\to\Rep(Q)$ is the natural functor.
\end{definition}
\begin{lemma}
  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to a representation of $\tilde Q$.
\end{lemma}
\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$. Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the one of $Q$. Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,w)$ of $\tilde Q$. This leads the claim. The statement for preinjective representations follows in the same way.
\end{proof}
We choose a map $d:\tilde Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$. In any case, we can consider the decomposition $X_q=\bigoplus_{w\in W_Q} X_{(q,w)}$. We define a torus action on each $X_{(q,w)}$ via $t.x_{(q,w)}=t^{d(q,w)}x_{(q,w)}$ which can be extended linearly to each $X_q$. For a fixed a subspace $U_q$, we can define the subspace $t.U_q$. In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$. Actually, for this the action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$ and every $x\in X_i$. 
\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
If $X\in\Rep(Q)$ can be lifted, $d:\tilde Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,w\alpha)-d(i,w)=c_\alpha$ for all $\alpha:i\to j$ and $w\in W_{Q}$.
\end{lemma}
\begin{proof} Let $U\in \Gr_\bfe(X)$. Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,w)}:X_{(i,w)}\to X_{(j,w\alpha)}$. Let $u_{(i,w)}\in U_{(i,w)}$ and $\alpha:i\to j\in Q_1$. Then we have $X_\alpha(u_{(i,w)})\in U_{(j,w\alpha)}$ because $X$ can be lifted to the universal cover. Then it follows
\[X_\alpha(t.u_{(i,w)})=X_\alpha(t^{d(q,w)}u_{(i,w)})=t^{d(q,w)}X_\alpha(u_{(i,w)})=t^{d(q,w)}u_{(j,w\alpha)}=t^{-c_\alpha}t.u_{(j,w\alpha)}\]
for some $u_{(j,w\alpha)}\in U_{(j,w\alpha)}$.
Now we have \[\bigoplus_{w\in W_Q} t.U_{(j,w)}=\bigoplus_{w\in W_Q}t^{c(j,w)}t.U_{(j,w)}\]
for every $t\in\C^\ast$ if $c(j,w)$ is constant. This yields  
\[t.U_j=\bigoplus_{w\in W_Q} t.U_{(j,w)}=\bigoplus_{w\in W_Q}t^{-c_\alpha}t.U_{(j,w)}\]
for every $t\in \C^\ast$.
\end{proof}

\begin{lemma} Let $X$ be an indecomposable representation of $\tilde Q$. There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that $d(i,w)\ne d(j,w')$ if $i\neq j$ or $w\neq w'$ and such that $d(j,w')-d(i,w)=c_\alpha$ if and only if $w'=w\alpha$ and $(i,w),\,(j,w\alpha)\in \mathrm{supp}(X)$. 
\end{lemma}
\begin{proof}
Since $X$ is finite-dimensional, $\mathrm{supp}( X)$ is a connected finite tree. In order to prove the statement, we assume that $d(q,1)=0$ and that $(q,1)\in \mathrm{supp}(X)$ and, moreover, fix the numbers $c_\alpha$ in such a way that the two conditions are satisfied. To do so, let $K$ be the maximal length of a path in $\mathrm{supp}(X)$. Let $|Q_1|=n$. Set $c_{\alpha_1}=1$ and inductively 
\[c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}.\]
Note that if $A_Q$ is the free abelian group in the generators $\alpha_1,\ldots,\alpha_n$ and $f:W_Q\to A_Q$ is the group homomorphism induced by $f(\alpha)=\alpha$ and $f(\alpha^{-1})=-\alpha$ and $g:A_Q\to \ZZ$ the one defined by $g(\alpha)=c_\alpha$ for all $\alpha\in Q_1$,  we have $d(q,w)=(g\circ f)(w)$ where $q$ is uniquely determined by $w$ on every connected component. In particular, we have
\[d(q,w)=\sum_{i=1}^nd_ic_{\alpha_i}\]
where $d_i$ counts the number of appearances of the arrow $\alpha_i$ in $w$ taking orientations into account. 
First note that we obviously have $d(j,w\alpha)-d(i,w)=c_\alpha$. Now assume that $d(i,w)=d(j,w')$ which means that $\sum_{i=1}^{n}d_ic_{\alpha_i}=\sum_{i=1}^{n}e_ic_{\alpha_i}$
which implies
\[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
Since we have $|d_i-e_i|\leq K$, we obtain $$|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|\leq K\sum_{i=1}^{n-1}c_{\alpha_i}<c_{\alpha_n}$$
This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_{i}}$. An analogous proof applies to show that $d(j,w')-d(i,w)\neq c_\alpha$ if $w'\neq w\alpha$ using that, actually, $c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}$.

\end{proof}
\begin{theorem}
  $Gr^Q_\bfe(X)^T\cong\bigsqcup_{\tilde\bfe of type \bfe} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$
\end{theorem}
